Meta-analysis

### 2020-07-07 04_MetaAnalysis.Rmd
add a wald test on Disease pressure moderator
Started at building a forest plot for the manuscript. Also a small analysis of indiect comparison data (to be deleted later)

@@

```{r compareDvNDP}
anova(PM_mv, PM_mv_Dp)
```

No significant difference which informs us to use the original model `PM_mv`, which is the simplest.

>>>>

Lets look at the trial variability in this model with a forest plot
```{r forestP, fig.height= 40, fig.width=10}
# If anyone knows how to fix the margins here it would be helpful!!!!!!!!!!!!!!!!
metafor::forest(PM_mv, cex =0.75 , width = 5,
                ilab = cbind(dat1$trial_ref, dat1$location, dat1$year, dat1$row_spacing, dat1$host_genotype, dat1$dose,
                             as.character(dat1$spray_management)),
                ilab.xpos = c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1),
                slab = NA, 
                xlim = c(-7, 3.5),
                ylim = c(4,119),
                xlab = "Grain yield mean difference")

### add text with Q-value, dfs, p-value, and I^2 statistic
text(-5.1, -0.8, pos=3, cex=0.75, bquote(paste("RE Model for All Studies (Q = ",
     .(formatC(PM_mv$QE, digits=2, format="f")), ", df = ", .(PM_mv$k - PM_mv$p),
     ", p = ", .(formatC(PM_mv$QEp, digits=3, format="f")), ") ")))

### add column headings to the plot
text(c(-6.5, -5.5,-4.75,-4.15,-3.4,-2.5,-1), 117.9,cex = 0.85, 
     c("Trial\nReference", "Location", "Year", "Row\nSpacing","Host\nCultivar","DMI dose","SM"),
     font = 2)

```

@@

```{r compareDvNDP}
AIC(PM_mv_Dp)
anova(PM_mv_Dp, btt = "D_pres")
anova(PM_mv, PM_mv_Dp)
```

A Wald test of `D_pres` shows the moderator is not significant in accounting for heterogeneity (P = 0.4859).
No significant difference which informs us to use the original model `PM_mv`, which is the simplest.

### Test for bias in indirect comparisons 
Treatments `Early` and `LatePlus` did not co-occur in any of the trials considered in the meta-analysis.
Indirect comparisons are ok to interpret in the results of a network meta-analysis, however if there are biases between trials including `Early` or `LatePlus` treatments then the results are likely bias. 
Therefore we wish to do a quick check that the trials which included `Early` treatments did not significantly differ from trials which incorportated `LatePlus`,
Lets create a data.frame of values for this comparison

```{r}
Ear <- 
   dat1 %>%
   filter(spray_management == "Early")%>%
   distinct(trial_ref)

LP <- 
   dat1 %>%
   filter(spray_management == "Late_plus")%>%
   distinct(trial_ref)

dat1$indirectC <- NA

dat1 %>%
   filter(trial_ref == Ear$trial_ref)

dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"
dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"

dat1 %>%
   filter(!is.na(indirectC))%>%
   ggplot(aes(x = indirectC, y = grain_MD))+
   geom_boxplot()

dat1 %>%
   filter(!is.na(indirectC),
          spray_management != "Early",
          spray_management != "Late_plus")%>%
   ggplot(aes(x = indirectC, y = grain_MD))+
   geom_boxplot()

dat1[dat1$trial_ref == LP$trial_ref, "indirectC"] <- "LP"
dat1[dat1$trial_ref == Ear$trial_ref, "indirectC"] <- "Ear"

dat2 <- dat1 %>%
   filter(!is.na(indirectC),
          spray_management != "Early",
          spray_management != "Late_plus")

table(dat2$spray_management, dat2$indirectC)

summary(aov(grain_MD ~ indirectC + spray_management + trial_ref, data = dat2))

```

This anova shows that there is no significant difference between the trials, spray_management or the specific trials with either `Early` or `Late_plus`. 
Therefore there is low risk that interpreting results from this indirect comparison between `Early` and `Late_plus`.
